ANCOVA Comparison Simulations: Discrete Outcomes

### 2018-03-21 simulations/continuous_outcomes.Rmd

plot_power_ratio_gamma <- function(powermat_list, gamma_vec, alpha, title){
  gamma_power_alpha <- t(sapply(powermat_list, function(x) x[floor(alpha*nrow(x)),]))
  colnames(gamma_power_alpha) <- c("ANCOVA", "Stratified Permutation", "Differenced Permutation", "LM Permutation", "Freedman-Lane")
  gamma_power_alpha <- apply(gamma_power_alpha, 2, function(x) x/gamma_power_alpha[,"ANCOVA"])
  melt(gamma_power_alpha, value.name="Power") %>%
  mutate("Method" = Var2) %>%
  mutate("Effect" = rep(gamma_vec, 5)) %>% 
  filter(Method != "Differenced Permutation") %>%
  filter(Method != "ANCOVA") %>%
  ggplot(aes(x = Effect, y = Power)) +
  geom_line(aes(color = Method))+
  xlab("Effect size") +
  ylab("Relative Power") +
  theme_bw() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 16),
    title = element_text(size = 16),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 14),
    strip.text.x = element_text(size = 12)
  ) 
}
```

@@

```{r plot_for_ms, include=FALSE}
p1 <- plot_power_ratio_gamma(gamma_power, tr_effect, 0.05, "Power at level 5%, Constant Treatment Effect") + 
  ylim(0, 1.2) +
  theme(legend.position="bottom") + 
  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
  report_theme +
  ggtitle("Constant Treatment \n Effect")

>>>>

plot_power_ratio_gamma <- function(powermat_list, gamma_vec, alpha, title){
  gamma_power_alpha <- t(sapply(powermat_list, function(x) x[floor(alpha*nrow(x)),]))
  colnames(gamma_power_alpha) <- c("ANCOVA", "Stratified Permutation", "Differenced Permutation", "LM Permutation", "Freedman-Lane")
  gamma_power_alpha <- apply(gamma_power_alpha, 2, function(x) x/gamma_power_alpha[,"ANCOVA"])
  melt(gamma_power_alpha, value.name="Power") %>%
  mutate("Method" = Var2) %>%
  mutate("Effect" = rep(gamma_vec, 5)) %>% 
  filter(Method != "Differenced Permutation") %>%
  filter(Method != "ANCOVA") %>%
  ggplot(aes(x = Effect, y = Power)) +
  geom_line(aes(linetype = Method))+
  xlab("Effect size") +
  ylab("Relative Power") +
  theme_bw() +
  theme(
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 16),
    title = element_text(size = 16),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 14),
    strip.text.x = element_text(size = 12)
  ) 
}
```

@@

```{r plot_for_ms, include=FALSE}
p1 <- plot_power_ratio_gamma(gamma_power, tr_effect, 0.05, "Power at level 5%, Constant Treatment Effect") + 
  ylim(0, 1.2) +
  theme(legend.position="bottom") + 
  guides(linetype=guide_legend(nrow=1,byrow=TRUE)) +
  report_theme +
  ggtitle("Constant Treatment \n Effect")

### 2018-03-21 simulations/discrete_outcomes.Rmd

```{r plot_for_ms, include=FALSE}
p1 <- plot_power_ratio_gamma(gamma_power, tr_effect, 0.05, "Power at level 5%, Constant Treatment Effect") + 
  ylim(0, 1.2 ) +
  theme(legend.position="bottom") + 
  guides(color=guide_legend(nrow=1,byrow=TRUE)) +
  report_theme +
  ggtitle("Constant Treatment \n Effect")

>>>>

```{r plot_for_ms, include=FALSE}
p1 <- plot_power_ratio_gamma(gamma_power, tr_effect, 0.05, "Power at level 5%, Constant Treatment Effect") + 
  ylim(0, 1.2 ) +
  theme(legend.position="bottom") + 
  guides(linetype=guide_legend(nrow=1,byrow=TRUE)) +
  report_theme +
  ggtitle("Constant Treatment \n Effect")
